\headingfont UNIVERSIDAD DE EXTREMADURA\\ FACULTAD DE CIENCIAS\\[1.5cm] \textbf{ Grado en Física\\ TRABAJO DE FIN DE GRADO\\[3.5cm]} {\setstretch{1.25}\flushleft{\large{\textbf{Developement of a FIWARE-based application for tree species monitoring (dendrometry)}}\\[3.5cm]}}

### 2020-07-03 docs/LaTex/Paper.tex
Minor fixes

In the other hand, LoRa can commonly refer to two distinct layers; a physical layer (LoRa itself) and a MAC layer protocol (LoRaWAN). The physical layer, is a proprietary technology developed by Semtech. So it is not fully open; LoRaWAN, however, is a protocol built to use LoRa physical layer, it is intended for sensor networks, wherein those sensors exchange packages with some server with a \enquote{low data rate and relatively long time intervals (one transmission per hour or even days).}\cite[p.~9]{LoRaGeneral}. This particularly means that LoRaWAN protocol is perfect for the purpose of this project.

@@

In the other hand, in order to this sketch takes advantage of the plugged LoRa Shield, is required to base it on the LoRaMAC-in-C library \cite{MCCI_lmic} (\cmd{arduino-lmic})\footnote{Dragino has its own \href{https://github.com/dragino/arduino-lmic}{fork of this library} but has been considered less upgraded than the MCCI version, which is a fork itself from the first port of LMIC library by \href{https://github.com/matthijskooijman}{Matthijs Kooijman}.} implemented by \href{https://mcci.com/}{MCCI}, whose technical documentation can be found in \cite{MCCI_lmic_docs}. The \cmd{arduino-lmic} library is, as its description in the README.md says, a port from the IBM LoRaWAN MAC in C, but \enquote{slightly modified to run in the Arduino environment allowing using the SX1272, SX1276 transceivers and compatible modules} \cite{MCCI_lmic}. The original IBM LoRaWAN MAC in C library was developed for microcontrollers in general, their examples and HAL ---Hardware Abstraction Layer or rather Hardware Annotation Library--- were only for STM32 MCUs (but bare-metal, so no Arduino on top).

@@

In the other hand \enquote{Any pins that are not needed should be specified as \cmd{LMIC\_UNUSED\_PIN}} as it can be also read in the \href{https://github.com/mcci-catena/arduino-lmic#pin-mapping}{Pin Mapping section} of the library \cmd{README.md}. As the reader can see, the example \ref{ej:pin_mapping} starts at line 76, that is because this is the line where the pin mapping is placed in the \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L76}{written sketch}.

>>>>

On the other hand, LoRa can commonly refer to two distinct layers; a physical layer (LoRa itself) and a MAC layer protocol (LoRaWAN). The physical layer, is a proprietary technology developed by Semtech. So it is not fully open; LoRaWAN, however, is a protocol built to use LoRa physical layer, it is intended for sensor networks, wherein those sensors exchange packages with some server with a \enquote{low data rate and relatively long time intervals (one transmission per hour or even days).}\cite[p.~9]{LoRaGeneral}. This particularly means that LoRaWAN protocol is perfect for the purpose of this project.

@@

On the other hand, in order to this sketch takes advantage of the plugged LoRa Shield, is required to base it on the LoRaMAC-in-C library \cite{MCCI_lmic} (\cmd{arduino-lmic})\footnote{Dragino has its own \href{https://github.com/dragino/arduino-lmic}{fork of this library} but has been considered less upgraded than the MCCI version, which is a fork itself from the first port of LMIC library by \href{https://github.com/matthijskooijman}{Matthijs Kooijman}.} implemented by \href{https://mcci.com/}{MCCI}, whose technical documentation can be found in \cite{MCCI_lmic_docs}. The \cmd{arduino-lmic} library is, as its description in the README.md says, a port from the IBM LoRaWAN MAC in C, but \enquote{slightly modified to run in the Arduino environment allowing using the SX1272, SX1276 transceivers and compatible modules} \cite{MCCI_lmic}. The original IBM LoRaWAN MAC in C library was developed for microcontrollers in general, their examples and HAL ---Hardware Abstraction Layer or rather Hardware Annotation Library--- were only for STM32 MCUs (but bare-metal, so no Arduino on top).

@@

On the other hand \enquote{Any pins that are not needed should be specified as \cmd{LMIC\_UNUSED\_PIN}} as it can be also read in the \href{https://github.com/mcci-catena/arduino-lmic#pin-mapping}{Pin Mapping section} of the library \cmd{README.md}. As the reader can see, the example \ref{ej:pin_mapping} starts at line 76, that is because this is the line where the pin mapping is placed in the \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L76}{written sketch}.
